% -------------------------
% Resume in Latex
% Author : Travis Trimboli
% Based off of: https://github.com/sb2nov/resume
% License : MIT
% ------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[4]{
  \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[nosep]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\Large Travis Trimboli}} & Email : \href{mailto:travis.trimboli@gmail.com}\\
%   \href{https://www.linkedin.com/in/travistrimboli/} & Mobile : +1-240-676-1232 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \bfseries Travis Trimboli} \\ \vspace{5pt}
  \small +1-240-676-1232 $|$ \href{mailto:travis.trimboli@gmail.com}{\underline{travis.trimboli@gmail.com}} $|$
  \href{https://www.linkedin.com/in/travistrimboli/}{\underline{linkedin.com/in/travistrimboli/}} $|$
\end{center}

% -----------SUMMARY-----------
\section*{Summary}
Accomplished cybersecurity professional with over 8 years of experience helping organizations improve their\
operations across all security domains. Experienced in combining software and security engineering\
to support the development of threat intelligence programs and security operations.\
Passionate about threat hunting, detection engineering, and vulnerability management, using threat\
intelligence to drive proactive security measures.

Proven track record of leveraging technical and domain\
knowledge from education, certifications, and experience to deliver value to customers.\
continued learning, and hands-on experience to deliver strategic and technical expertise through\
all stages of program development. Skilled at providing creative, customer-centric, outcome-oriented\ 
solutions, and passionate about building collaboration between cross-functional teams and stakeholders\ 
to align vision with needs.

% --------SKILLS------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: Python, SQL, GraphQL, YAML, Bash, JavaScript} \\ \vspace{1pt}
        \textbf{Development Tools}{: Atlassian (JIRA, Bitbucket, Confluence), Git, Ansible, Terraform, Postman, Kubernetes, Docker} \\ \vspace{1pt}
        \textbf{Cloud Platforms}{: AWS, Azure, Google Cloud Platform} \\ \vspace{1pt}
        \textbf{Data and Security}{: Splunk, Sentinel, Elastic, Pandas, Matplotlib, {MITRE ATT\&CK}, Crowdstrike, STIX/TAXII } \\ \vspace{1pt}
        \textbf{Management}{: Salesforce, Gainsight, ChurnZero, Pendo, Aha!} 
        }}
\end{itemize}

% -----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{CareFirst BlueCross Blue Shield}{Baltimore, MD / Remote}
{Senior Cybersecurity Analyst - Threat Intelligence}{May 2025 -- Present}
\resumeItemListStart
\item Supported the development of the CareFirst Threat Intelligence Service program with tasks including:
\begin{itemize}[nosep]
  \item Advised smaller subsidiaries and clients on developing their security operations and threat intelligence programs.
  \item Adapted new tools and technologies to streamline processes and improve efficiency.
  \item Performed monitoring and analysis of threat intelligence data to identify trends and patterns.
  \item Produced actionable intelligence reports and briefings for stakeholders.
\end{itemize}
\item Managed threat intelligence operations, including threat hunting, detection engineering, and vulnerability management.
\item Actively participated in threat landscape and attack surface analysis to identify emerging threats and vulnerabilities.
\item Identified areas where threat intelligence can play an active role in improving organizational posture\
across multiple security domains from network and endpoint to the cloud.
\item Actively collaborated with security teams on threat intelligence program strategy including but not limited to:
\begin{itemize}[nosep]
  \item Establishing intelligence requirements.
  \item Creating useful workflows.
  \item Broadening cross-team collaboration.
  \item Executing on the creation, implementation, and integration of new tools and processes..
\end{itemize}
\item Developed custom tools including, a vulnerability prioritization system that uses various data points, including the\
NIST Likely Exploited Vulnerability (LEV) metric, and a threat actor analysis tool to analyze and visualize\
threat actor techniques, tactics, and procedures (TTPs).
\resumeItemListEnd

\resumeSubheading
{ThreatQuotient}{Reston, VA / Remote}
{Customer Success Engineer}{Feb 2019 -- May 2025}
\resumeItemListStart
\item Guided the development of the Customer Success program from the outset with tasks including:
\begin{itemize}[nosep]
  \item Advised in defining the Customer Success Engineer role and responsibilities.
  \item Helped determine the operational, tactical, and strategic approaches applied by the team.
  \item Introduced customer success metrics and KPIs and ways to track them.
  \item Adapted new tools and technologies to streamline processes and improve efficiency.
\end{itemize}
\item Managed North American customers, including commercial, federal, and DoD, as a trusted advisor to SMBs\
and enterprise-level organizations comprising the Fortune 50, 100, and 500 lists.
\item Advised stakeholders from the C-Suite to the primary contributor level on developing their\
security operations and threat intelligence programs.
\item Identified areas where CTI can play an active role in improvising organizational posture\
across multiple security domains from network and endpoint to the cloud.
\item Actively collaborated with security teams on CTI program strategy including but not limited to:\
establishing intelligence requirements, creating useful workflows, broadening cross-team collaboration,\
executing on the implementation and integration of new tools and processes, and taking full advantage\
of the platform to improve decision-making in critical situations.
\item Contributed to custom integration and tool development to increase customer operational efficiencies.
\item Delivered security program recommendations based on established frameworks such as {MITRE ATT\&CK},\
Palantir ADS, NIST CSF, and various compliance standards depending on industry.
\resumeItemListEnd

\resumeSubheading
{Carbon Black}{Boulder, CO}
{Threat Analyst}{Aug 2018 -- Feb 2019}
\resumeItemListStart
\item Participated in a 24/7 SOC team working on rotating schedules.
\item Performed endpoint security monitoring, security event triage, and incident response for a mid-size organization.
\item Collaborated with other team members and management to document and report incidents to stakeholders.
\item Maintained records of investigated security events and incident response activities utilizing case management and ticketing systems.
\item Took on security operations responsibilities when not on active SOC shifts, including documentation, basic malware analysis,\
exceptions tracking, security tool management, tuning, configuration, and metrics and reporting.
\item Contributed to the development of front-end applications to support SOC team operations.
\resumeItemListEnd

\break
\resumeSubSubheading
{}{Waltham, MA}
{Sales Engineer}{Oct 2017 -- Aug 2018}
\resumeItemListStart
\item Configured and presented product demonstrations for prospects, customers, and partners.
\item Served as a client-facing technical resource supporting the sales organization.
\item Completed product RFI/RFPs for all three products as they present themselves.
\item Coordinated product evaluations and proof of concepts for prospects.
\item Assisted product management with documenting usability and feature feedback.
\item Supported prospect and customer implementations and continued success using the products.
\item Provided internal support for any troubleshooting-related inquiries.
\item Examined potential threats and provided analysis on how each product would respond.
\resumeItemListEnd

\resumeSubheading
{Fidelis Cybersecurity}{Bethesda, MD}
{Account Manager}{Feb 2016 -- Oct 2017}
\resumeItemListStart
\item Conducted outbound and inbound B2B prospecting by phone and email for potential Commercial, Government, Defense, and Channel clients.
\item Communicated core value propositions of Fidelis products and services to C-suite individuals of all industries.
\item Qualified prospects based on needs, timelines, and budgets for the outside account team.
\item Accelerated prospects through the sales cycle, promoting revenue-generating outcomes.
\item Attended trade shows and partner functions to represent Fidelis, showcasing product components and gathering user feedback.
\resumeItemListEnd

\resumeSubHeadingListEnd

% -----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Maryland Global Campus}{Adelphi, MD}
{Master of Science in Information Technology; GPA: 4.00}{Aug 2017 -- May 2020}
\resumeSubheading
{University of Maryland}{College Park, MD}
{Bachelor of Arts; GPA: 3.80}{Aug 2008 -- May 2013}
\resumeSubHeadingListEnd

% --------Certifications------------
\section{Certifications}
\setlist[itemize]{leftmargin=*}
\begin{itemize}[nosep]
  \item Certified Information Systems Security Professional (CISSP)
  \item AWS Certified Cloud Practitioner
  \item CompTIA Secuiryt+
\end{itemize}

% -----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{Vulnerability Evaluation System (VES)}
{Vulnerability prioritization system that uses various data points, including the NIST Likely Exploited Vulnerability (LEV) metric,\
to assess vulnerabilities and calculate a unique VES score.}
\resumeSubItem{TTP Analyzer}
{Python application for parsing threat intelligence reports and analyzing MITRE ATT\&CK Tactics, Techniques, and Procedures (TTPs)\
to understand threat actor evolution over time.}
\resumeSubHeadingListEnd

% -------------------------------------------
\end{document}